Stimuli

### 2022-06-28 docs/00_participants.Rmd
Add tests

```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_tab <- participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	)

@@

```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp, test_language) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		test_language = md("**Language**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	as_raw_html()
```

```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed", colour = "black") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90),
		panel.grid.major.x = element_blank()
	) 
```

@@

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	filter(valid_participant) %>% 
	mutate(age_group = str_remove(age_group, " months")) %>%
	ggplot(aes(age_group, participant, colour = lp)) +
	facet_grid(~location, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Lang. Pofile") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	)
```

>>>>

```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_tab <- participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	drop_na(valid_participant) %>% 
	count(age_group, lp, valid_participant) %>% 
	pivot_wider(
		names_from = c("age_group", "valid_participant"),
		values_from = c("n"), 
		values_fill = 0
	) %>% 
	mutate(
		`21 months` = paste0(`21 months_TRUE`, " (", `21 months_FALSE`, ")"),
		`25 months` = paste0(`25 months_TRUE`, " (", `25 months_FALSE`, ")"),
		`30 months` = paste0(`30 months_TRUE`, " (", `30 months_FALSE`, ")")

	) %>% 
	select(-c(ends_with("TRUE"), ends_with("FALSE"))) %>% 
	gt() %>% 
	tab_header(
		title = "Testing sessions",
		subtitle = "Invalid testing sessions are shown between parentheses"
	) %>%
	cols_label(
		lp = "",
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	tab_style(
		style = list(
			cell_text(weight = "bold"),
			cell_fill("grey82")
		),
		locations = list(
			cells_row_groups()
		)
	)

@@

```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_tab <- participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	drop_na(valid_participant) %>% 
	count(age_group, lp, test_language, valid_participant) %>% 
	pivot_wider(
		names_from = c("age_group", "valid_participant"),
		values_from = c("n"), 
		values_fill = 0
	) %>% 
	mutate(
		`21 months` = paste0(`21 months_TRUE`, " (", `21 months_FALSE`, ")"),
		`25 months` = paste0(`25 months_TRUE`, " (", `25 months_FALSE`, ")"),
		`30 months` = paste0(`30 months_TRUE`, " (", `30 months_FALSE`, ")")

	) %>% 
	select(-c(ends_with("TRUE"), ends_with("FALSE"))) %>% 
	gt(groupname_col = "lp") %>% 
	cols_label(
		lp = md("**Language profile**"),
		test_language = "",
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	tab_style(
		style = list(
			cell_text(weight = "bold"),
			cell_fill("grey82")
		),
		locations = list(
			cells_row_groups()
		)
	)

```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(lp))) +
	facet_grid(~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed", colour = "black") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "none",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90),
		panel.grid.major.x = element_blank()
	) 
```

@@

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	filter(valid_participant) %>% 
	count(participant, age_group) %>% 
	pivot_wider(
		id_cols = participant,
		names_from = age_group,
		values_from = n,
		values_fill = 0
	) %>% 
	pivot_longer(
		2:4,
		names_to = "age_group",
		values_to = "n"
	) %>% 
	ggplot() +
	aes(
		age_group,
		participant,
		fill = as.factor(n)
	) + 
	geom_tile(
		colour = "white"
	) +
	labs(
		x = "Age (months)", 
		y = "Exposure to 2nd language", 
		fill = "Lang. Pofile"
	) +
	scale_fill_manual(values = c("white", pal_d3()(2)[2])) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_text(size = 7),
		axis.ticks.y = element_blank()
	)

ggsave(
	here("img", "participants_longitudinal.png"),
	height = 15,
	width = 1.5
)

### 2022-06-28 docs/01_stimuli.Rmd
Add tests

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
	ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)

@@

theme_set(theme_minimal()) # in utils.R
```

@@

```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
	# geom_jitter(colour = "white", size = 1, shape = 1,
	# 			width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
	# geom_jitter(colour = "black", size = 1, shape = 1,
	# 			width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
		panel.grid.major.x = element_blank()

	)
```

@@

```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
means <- stimuli %>% 
	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	group_by(test_language, location, trial_type) %>% 
	summarise(
		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
		.groups = "drop"
	) %>% 
	drop_na()

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type,
			   xmin = familiarity_prime-familiarity_se_prime, xmax = familiarity_prime-familiarity_se_prime)) +
	facet_wrap(location~test_language, scales = "free_y") +
	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
	# geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Prime word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 7),
		axis.title.y = element_blank(),
		panel.grid.major.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6.5, out.width="100%"}
means <- stimuli %>% 
	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	group_by(test_language, location, trial_type) %>% 
	summarise(
		familiarity_target = mean(familiarity_target, na.rm = TRUE),
		.groups = "drop"
	)

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language, scales = "free_y") +
	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
	# geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Target word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	# scale_y_reordered() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 7),
		axis.title.y = element_blank(),
		panel.grid.major.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

animacy <- stimuli %>%
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
	count(location, test_language, trial_type, role, is_animate) %>% 
	drop_na(is_animate) %>% 
	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(location~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(location~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() +

@@

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
	drop_na(trial_type, category) %>% 
	count(trial_type, test_language, location, role, category) %>% 
	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
	facet_wrap(role~location~test_language) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "% of trials", y = "Trial type",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
		panel.grid = element_blank()

	)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = pal_d3()(4),
	ggplot2.discrete.colour = pal_d3()(4)
)

@@

theme_set(theme_custom()) # in utils.R
```

@@

```{r stimuli_frequency_childes_prime, echo=FALSE, fig.height=5, message=FALSE, warning=FALSE, out.width="80%", paged.print=TRUE}

stimuli %>% 
	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot() +
	aes(
		x = trial_type, 
		y = frequency_prime_childes, 
		colour = trial_type, 
		fill = trial_type
	) +
	facet_wrap(~test_language) +
	geom_boxplot(
		colour = "black",
		fill = "white", 
		size = 1, 
		outlier.colour = NA,
		width = 0.1
	) + 
	geom_point(
		shape = 1, 
		stroke = 1.25,
		size = 3,
		position = position_jitter(
			width = 0.1,
			seed = 888
		)
	) +
	labs(
		x = "Trial type", 
		y = "Lexical frequency (Zipf score)",
		colour = "Trial type", 
		fill = "Trial type"
	) +
	theme(
		legend.position = "none",
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
	)

ggsave(here("img", "stimuli_frequency_prime_childes.png"))

@@

```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
stimuli %>% 
	distinct(
		test_language, 
		target,
		prime,
		.keep_all = TRUE
	) %>% 
	ggplot() +
	aes(
		x = trial_type, 
		y = frequency_target_childes, 
		colour = trial_type,
		fill = trial_type
	) + 
	facet_wrap(~test_language) +
	geom_boxplot(
		colour = "black", 
		fill = "white",
		size = 1,
		outlier.colour = NA, 
		width = 0.1
	) +
	geom_point(
		shape = 1, 
		stroke = 1.25,
		size = 3,
		position = position_jitter(
			width = 0.1,
			seed = 888
		)
	) +
	labs(
		x = "Trial type",
		y = "Lexical frequency (Zipf score)",
		colour = "Trial type",
		fill = "Trial type"
	) +
	theme(
		legend.position = "none",
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
	)

ggsave(here("img", "stimuli_frequency_target_childes.png"))

@@

```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
means <- stimuli %>% 
	distinct(test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	group_by(test_language, trial_type) %>% 
	summarise(
		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
		.groups = "drop"
	) %>% 
	drop_na()

stimuli %>% 
	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
	ggplot() +
	aes(
		familiarity_prime, 
		reorder(prime, familiarity_prime),
		colour = trial_type, 
		fill = trial_type,
		xmin = familiarity_prime-familiarity_se_prime,
		xmax = familiarity_prime+familiarity_se_prime
	) +
	facet_wrap(~test_language, scales = "free_y") +
	geom_vline(
		data = means, 
		aes(
			xintercept = familiarity_prime, 
			colour = trial_type
		),
		size = 1
	) +
	geom_errorbar(width = 0) +
	geom_point() +
	labs(
		x = "% of infants that understand",
		y = "Prime word",
		colour = "Trial type", 
		fill = "Trial type"
	) +
	scale_x_continuous(
		labels = percent,
		limits = c(0, 1)
	) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.y = element_text(size = 7),
		axis.title.y = element_blank(),
		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)

ggsave(here("img", "stimuli_familiarity_prime.png"))

@@

```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6.5, out.width="100%"}
means <- stimuli %>% 
	distinct(test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	group_by(test_language, trial_type) %>% 
	summarise(
		familiarity_target = mean(familiarity_target, na.rm = TRUE),
		.groups = "drop"
	)

stimuli %>% 
	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot() +
	aes(
		x = familiarity_target, 
		y = reorder(target, familiarity_target), 
		colour = trial_type,
		fill = trial_type,
		xmin = familiarity_target-familiarity_se_target,
		xmax = familiarity_target+familiarity_se_target
	) +
	facet_wrap(
		~test_language, 
		scales = "free_y"
	) +
	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(
		data = means,
		aes(
			xintercept = familiarity_target,
			colour = trial_type
		), 
		size = 1
	) +
	geom_errorbar(width = 0) +
	geom_point(
		shape = 1,
		size = 0.5,
		stroke = 1
	) +
	labs(
		x = "% of infants that understand",
		y = "Target word",
		colour = "Trial type",
		fill = "Trial type"
	) +
	scale_x_continuous(
		labels = percent,
		limits = c(0, 1)
	) +
	# scale_y_reordered() +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.y = element_text(size = 7),
		axis.title.y = element_blank(),
		panel.grid.major.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)
ggsave(here("img", "stimuli_familiarity_target.png"))

@@

animacy <- stimuli %>%
	distinct(
		test_language, 
		target, 
		prime, 
		.keep_all = TRUE
	) %>% 
	pivot_longer(
		c(is_animate_prime, is_animate_target), 
		names_to = "role",
		values_to = "is_animate"
	) %>% 
	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
	count(
		test_language, 
		trial_type,
		role,
		is_animate
	) %>% 
	drop_na(is_animate) %>% 
	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot() +
	aes(
		x = trial_type, 
		y = n, 
		fill = is_animate,
		colour = is_animate
	) + 
	facet_wrap(~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(
		yintercept = 0.5, 
		size = 1,
		colour = "grey"
	) +
	labs(
		title = "Prime", 
		x = "Trial type", 
		y = "# trials",
		colour = "Animacy", 
		fill = "Animacy"
	) +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() +

@@

ggsave(here("img", "stimuli_animacy.png"))

@@

stimuli %>% 
	distinct(
		test_language, 
		target, 
		prime,
		.keep_all = TRUE
	) %>% 
	pivot_longer(
		c(category_prime, category_target),
		names_to = "role",
		values_to = "category"
	) %>% 
	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
	drop_na(
		trial_type,
		category
	) %>% 
	count(
		trial_type, 
		test_language, 
		role, 
		category,
		name = "sum"
	) %>% 
	right_join(
		expand(
			.,
			trial_type, 
			test_language, 
			role, 
			category
		)
	) %>%
	replace_na(list(sum = 0)) %>% 
	group_by(trial_type, test_language, role) %>% 
	mutate(
		n =  sum(sum),
		prop = sum/n
	) %>% 
	ungroup() %>% 
	ggplot() +
	aes(
		x = prop,
		y = reorder_within(category, desc(prop), list(trial_type, role, test_language)),
		fill = test_language,
		order = prop
	) + 
	facet_wrap(
		trial_type~role~test_language,
		scales = "free_y", labeller = label_wrap_gen(multi_line = FALSE)
	) +
	geom_col(
		colour = "white",
		position = position_dodge(),
		width = 1
	) +
	labs(
		x = "% of trials",
		y = "Trial type",
		colour = "Trial type",
		fill = "Trial type"
	) +
	scale_fill_d3(palette = "category10") +
	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
	scale_y_reordered() +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text.y = element_text(size = 9, hjust = 1),
		axis.text.x = element_text(size = 8, hjust = 1),
		axis.title.y = element_blank(),
		axis.ticks.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		strip.text = element_text(size = 10)
	)

ggsave(here("img", "stimuli_animacy.png"), width = 15)
